---
output: 
  pdf_document:
    latex_engine: xelatex
    keep_tex: TRUE
    includes:
      in_header: ContractTemplateHeader.tex
editor_options: 
  chunk_output_type: console
fontsize: 11pt
mainfont: Times New Roman
geometry: margin=1in
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(pander)
```

```{r document_setup}
#client information
client_organization <- ""
client_organization_abb <- ""
client_name <- ""

# project information
project_lead <- ""
project_tagline <- ""
project_desc <- ""
project_desc2 <- ""
project_completion <- ""
project_rate <- 

# Objectives
Obj1 <- ""
Obj2 <- ""
Obj3 <- ""
Obj4 <- ""
```



This agreement contains the entire understanding entered into between DAPPER, LLC (DAPPER) and `r client_organization` (`r client_organization_abb`) for the purposes of `r project_tagline`. Any change to this agreement must be in writing and signed by both parties. 

This contract takes effect when all appropriate signatures are applied, at which point which DAPPER shall commence performance of duties as set forth. This contract will be completed upon `r project_completion`.

## DESCRIPTION OF CONTRACT
This contract is for services as requested of DAPPER by `r client_organization` and `r client_name` from the date upon which this contract is signed by both parties to the date of completion. During that period, DAPPER will be paid `r paste0("$", project_rate, "/hr")` to `r project_desc`. 

## SERVICES PROVIDED
DAPPER will work collaboratively with `r client_name` for the purposes of `r project_desc2`. Specifically, DAPPER commits to the following milestones:

1. `r Obj1` 
2. `r Obj2` 
3. `r Obj3` 
4. `r Obj4` 

If at any time, these milestones need to be changed, both parties must agree (by signature) to new milestones. Either `r client_organization_abb` or DAPPER may request a change to the milestones. A request must be submitted in writing to the other party, and the recipient of the request has 10 business days to either accept or reject the request.

## REMUNERATION 
`r client_organization_abb` agrees to payment of DAPPER for the purposes of the work outlined above. `r client_organization_abb` will remunerate DAPPER according to the following timeline, in association with the specific milestones outlined in *SERVICES PROVIDED*.

\newpage
```{r}

Service <- c(Obj1, Obj2, Obj3, Obj4)
est.time <- c(4,10,10,16)
due.date <- c("-", "-", "-", "-")
est.cost <- est.time * project_rate
table <- data.frame(Service, est.time, est.cost, due.date)
colnames(table) <- c("Service","Est. Time", "Est. Cost", "Due Date")

pander(table, style = "grid", justify = c("left","center","center","center"), 
       split.cells = c(35,10,10,10), use.hyphening = TRUE)
```

For the purposes of this contract DAPPER and `r client_organization_abb` agree to an hourly rate of `r paste0("$", project_rate)` and a total maximum billed cost of `r paste("$", sum(est.cost))`. At the completion of each milestone, DAPPER will provide `r client_organization_abb` with an invoice of sufficient detail for billing purposes. Payment must be received by DAPPER within 30 days of invoice delivery. Failure to deliver timely payment is a violation of this contract, will lead to interest charges (1.5% per month), and may result in contract termination.

	Payment should be made to:

		DAPPER
		c/o Juniper Simonis
		3519 NE 15th Ave. Ste. 467
		Portland, OR 97212

## DATA
DAPPER agrees to abide by the data protocols and regulations of `r client_name`  and `r client_organization_abb` for the purposes of this contract. 

## TERMINATION
Either party may terminate this Agreement by giving 10 business days' written notice to the other of such termination. 

If work is terminated at the request of `r client_organization_abb`, DAPPER retains the right to remuneration for services provided prior to that request. Within 10 days of receiving the termination request DAPPER shall provide a final invoice sufficiently detailing work prior to the request to `r client_organization_abb`. `r client_organization_abb` shall accept or reject the invoice within 10 days. Upon `r paste0(client_organization_abb, "'s")` written acceptance of a final invoice, DAPPER shall return payment in excess of the invoice total to `r client_organization_abb` within 10 days.

If work is terminated at the request of DAPPER, any payments made by `r client_organization_abb` in amounts beyond the value of work completed shall be refunded to `r client_organization_abb`. At the time of the termination request, DAPPER shall provide a final invoice sufficiently detailing work prior to the request within 10 days to `r client_organization_abb`. `r client_organization_abb` shall accept or reject the invoice within 10 days. Upon `r paste0(client_organization_abb,"'s")` written acceptance of a final invoice, DAPPER shall return payment in excess of the invoice total to `r client_organization_abb` within 30 days.

If work is terminated by either party, rights to completed work shall transfer to `r print(client_organization_abb)` and `r client_name`, and DAPPER shall retain rights to work completed on or before termination date for portfolio use. Source files for work completed prior to termination will be transferred to `r client_organization_abb` and `r client_name` by request.

## SIGNATURES
**The parties signing below agree to all terms and conditions contained in this Agreement and warrant that they have full authority to execute this agreement and perform their respective obligations.**  

&nbsp; 

\noindent\rule{6cm}{0.4pt}
**Juniper Simonis, PhD**  
*Lead Scientist*, DAPPER, LLC  

&nbsp;  

\noindent\rule{6cm}{0.4pt}
**`r client_name`**  
`r client_organization`
